Object-Oriented Internet - Azure Interoperability

### 2020-12-03 Latex/Manuscript.tex
Final review of the latex text #37
- fixed formatting
- replaced Industrial IoT by IoT Central.

      The proposals are backed by proof of concept reference implementations confirming the possibility to interconnect selected cloud services with the cyber-physical system interconnected as one whole atop of the OPC UA by applying the proposed architecture and deployment scenario. It is contrary to interconnecting cloud services with a selected OPC UA server limiting the PubSub role to data export only.

@@

This article addresses further research on the integration of the CPS in the context of new emerging disciplines, i.e.~Industry 4.0 (I4.0) and the Industrial Internet of Things (IIoT). The new architecture is proposed for integration of the multi-vendor \textbf{machine-centric} CPS designed atop of M2M reactive communication and emerging cloud computing as a \textbf{human-centric} front-end. To support the multi-vendor environment OPC Unified Architecture \cite{LiteratureSurveyOnOpenPlatformCommunications} interoperability standard has been selected. The proposals are backed by proof of concept reference implementations. Prototyping addresses Microsoft Azure Cloud as an example. The prototyping outcome has been just published on GitHub as the open-source (MIT licensed) \todo{Add reference}. The proposed solutions have been harmonized with the more general concept called the Object-Oriented Internet.

@@

The \textit{IoT\ Central} service provides a process data visualization
user interface. To make this interface meaningful metadata called device
template is used to describe devices.

@@

It is worth stressing that interaction of the offered by the Azure
services can be configured flexibly, and as a result, the presented
above selection of services must be recognized as an example only. The
\textit{IoT\ Central} can be also seamlessly integrated with other
services as needed. The following services could also be considered to
build cloud-based automation solution:

@@

In \textit{IoT\ Central} a CPS is represented as a set
of devices. The characteristics and behavior of each device kind are
described by the device template. This Device Template (DT) contains
also metadata describing the data exchanged over the
wire with the CPS called Device Capability Model
(DCM). Additionally, the DT contains properties, customization, and
views definitions used by the service locally. As an option, DCM
expressed as a JSON-LD can be imported into a Device Template.
\textit{IoT\ Central} allows also to create and edit a DCM using the
dedicated web UI. A JSON file containing DCM can be derived from an
information model used as a foundation to establish the semantic-context
applied to achieve interoperability of the devices interconnected as the
CPS. DCM development against any external information
model is a design-time task and should be supported by dedicated
development tools. In any case, the data interchanged between the cloud
and the gateway must be compliant with the DCM, hence the middleware
software must be aware of conversions that must be applied to achieve
this interoperability.

@@

From the cloud side, it is proposed to employ the \textit{IoT\ Hub}
service to handle the network traffic targeting the cyber-physical
system. This service offers profiles of the AMQP, MQTT and HTTPS protocol
stacks. In any case, process data is transparently
transferred back-and-forth to the upper layer \textit{IoT\ Central}
service. Hence, the payload formatting is determined by the DCM
associated with the \textit{IoT\ Central} solution.

@@

Nowadays, the macro optimization of the industrial processes requires an integration of a vast variety of distributed applications provided by the Information and Communication Technology. It requires further research on the integration of \textbf{machine-centric} Cyber-Physical Systems (CPS) with \textbf{human-centric} front-end in the context of new emerging disciplines, i.e. Industry 4.0 and the Industrial Internet of Things (Sect. \ref*{introduction}).

@@

Concluding, the paper describes a proof of the concept that applying the proposed architecture and deployment scenario it is possible to interconnect selected cloud services (e.g. \textbf{Azure\ Industrial\ IoT}) with the \emph{Cyber-physical network} interconnected as one whole atop of the OPC UA PubSub. It is in contrast to interconnecting cloud services with the selected \emph{ Address\ Space} exposed by a selected OPC UA server limiting the PubSub role to data exporter transferring the data out of the OPC UA ecosystem.

>>>>

      The proposals are backed by proof of concept reference implementations confirming the possibility to integrate selected cloud services with the cyber-physical system interconnected as one whole atop of the OPC UA by applying the proposed architecture and deployment scenario. It is contrary to interconnecting cloud services with a selected OPC UA server limiting the PubSub role to data export only.

@@

This article addresses further research on the integration of the CPS in the context of new emerging disciplines, i.e.~Industry 4.0 (I4.0) and the Internet of Things (IoT). The new architecture is proposed for integration of the multi-vendor \textbf{machine-centric} CPS designed atop of M2M reactive communication and emerging cloud computing as a \textbf{human-centric} front-end. To support the multi-vendor environment OPC Unified Architecture \cite{LiteratureSurveyOnOpenPlatformCommunications} interoperability standard has been selected. The proposals are backed by proof of concept reference implementations. Prototyping addresses Microsoft Azure Cloud as an example. The prototyping outcome has been just published on GitHub as the open-source (MIT licensed) \todo{Add reference}. The proposed solutions have been harmonized with the more general concept called the Object-Oriented Internet.

@@

The \textbf{IoT\ Central} service provides a process data visualization
user interface. To make this interface meaningful metadata called device
template is used to describe devices.

@@

It is worth stressing that interaction of the offered by the Azure
services can be configured flexibly, and as a result, the presented
above selection of services must be recognized as an example only. The
\textbf{IoT\ Central} can be also seamlessly integrated with other
services as needed. The following services could also be considered to
build cloud-based automation solution:

@@

In \textbf{IoT\ Central} a CPS is represented as a set
of devices. The characteristics and behavior of each device kind are
described by the device template. This Device Template (DT) contains
also metadata describing the data exchanged over the
wire with the CPS called Device Capability Model
(DCM). Additionally, the DT contains properties, customization, and
views definitions used by the service locally. As an option, DCM
expressed as a JSON-LD can be imported into a Device Template.
\textbf{IoT\ Central} allows also to create and edit a DCM using the
dedicated web UI. A JSON file containing DCM can be derived from an
information model used as a foundation to establish the semantic-context
applied to achieve interoperability of the devices interconnected as the
CPS. DCM development against any external information
model is a design-time task and should be supported by dedicated
development tools. In any case, the data interchanged between the cloud
and the gateway must be compliant with the DCM, hence the middleware
software must be aware of conversions that must be applied to achieve
this interoperability.

@@

From the cloud side, it is proposed to employ the \textit{IoT\ Hub}
service to handle the network traffic targeting the cyber-physical
system. This service offers profiles of the AMQP, MQTT and HTTPS protocol
stacks. In any case, process data is transparently
transferred back-and-forth to the upper layer \textbf{IoT\ Central}
service. Hence, the payload formatting is determined by the DCM
associated with the \textbf{IoT\ Central} solution.

@@

Nowadays, the macro optimization of the industrial processes requires an integration of a vast variety of distributed applications provided by the Information and Communication Technology. It requires further research on the integration of \textbf{machine-centric} Cyber-Physical Systems (CPS) with \textbf{human-centric} front-end in the context of new emerging disciplines, i.e. Industry 4.0 and the Internet of Things (Sect. \ref*{introduction}).

@@

Concluding, the paper describes a proof of the concept that applying the proposed architecture and deployment scenario it is possible to integrate selected cloud services (e.g. \textbf{Azure\ IoT\ Central}) with the \emph{Cyber-physical network} interconnected as one whole atop of the OPC UA PubSub. It is in contrast to interconnecting cloud services with the selected \emph{ Address\ Space} exposed by a selected OPC UA server limiting the PubSub role to data exporter transferring the data out of the OPC UA ecosystem.
